data wrangling and plots

### 2021-04-06 shared analysis files /data_wrangling_plot.Rmd
contour plot craziness

```{r, echo=FALSE, results = 'hide', message=FALSE}
## loading libraries 
pacman::p_load(metafor, tidyverse, viridis, ggsci, plotly)
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE,build_vignettes = TRUE)
#library(orchaRd)

@@

```{r}
#with interaction term 
full_rf_model<-rma.mv(yi, vi, data=dat_MA_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level, 
               random = ~1 | experiment_id/ study_id/ response_id,
                 method="REML") 
full_rf_model

@@

>>>>

```{r, echo=FALSE, results = 'hide', message=FALSE}
## loading libraries 
pacman::p_load(metafor, tidyverse, viridis, ggsci, plotly,  mgcv)
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE,build_vignettes = TRUE)
#library(orchaRd)

@@

```{r}
#with interaction term 
full_rf_model<-rma.mv(yi, vi, data=dat_MA_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_rf_model

@@

```{r}
fig <- plot_ly(
  x = normalized$mean_temp_constant, 
  y = normalized$flux_range, 
  z = normalized$yi, 
  type = "contour", 
  contours = list(
    start = -19.42062,
    end = 5.286697,
    size = 1, 
    coloring = 'heatmap'
))
fig

#GAM APPROACH
#fit GAM
gam1<-gam(yi~te(mean_temp_constant,flux_range,k=6),data=normalized) # note, lots of decisions that I blew by here
summary(gam1)
#estimate values via gam
vals<-expand.grid(flux_range=seq(0,20,length.out = 100), mean_temp_constant=seq(0,35,length.out = 100))
pd.gam<-predict(gam1,newdata=vals)
surf<-data.frame(vals,value=pd.gam)
#plot values as a surface
# setting up custom color palette for surfaces, or anything besides the default green/ yellow one
or2<-c('#fdd49e','#fdbb84','#fc8d59','#e34a33','#b30000')
or2.bl2.pal<-c(colorRampPalette(colors=or2)(100))
#plot gam surface
ggplot(surf,aes(x=mean_temp_constant,y=flux_range,z=value))+
  geom_raster(aes(fill=value))+
  #geom_abline(intercept=0,slope=1,linetype=2)+
  geom_contour(colour=gray(0.2),binwidth=0.5,size=0.2)+
  #geom_contour(colour='black',breaks=c(mean(surf$value)),size=2)+
  #geom_point(data=sample.locs,alpha=0.5)+
  geom_contour(colour="black",breaks=c(0),size=2)+
  scale_x_continuous('Mean Temp (°C)',expand=c(0,0))+
  scale_y_continuous('Temp Range (°C)',expand=c(0,0))+
  scale_fill_gradientn('Size',
                       colors= or2.bl2.pal,
                       breaks=seq(-2,5,2),limits=c(-2,5),
                       guide = guide_colourbar(ticks.colour = gray(.2),
                                               ticks.linewidth = 1.,
                                               frame.colour = "black"))+
  coord_cartesian(xlim=c(0,35),ylim=c(0,20))+
  theme_bw()

max(normalized$yi)

```
